A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-10-06 paper/paper.tex
completed RL-PC passage

The vmPFC subserves less ambiguous subjective-value-related evaluative processes
reward-informed and risk estimation of self-relevant environmental stimuli.
This DMN node is more closely associated with
orchestrating adapted behavior by bottom-up-driven
processing of “what matters now”.
Quantative lesion findings across 344 human individuals confirmed
a gross impairment in value-based decision making
(Glaescher et al., 2016).
The vmPFC is preferentially connected with limbic and reward-related areas.
The vmPFC has been observed to have monosynaptical connections
with the nucleus accumbens
in axonal tracing studies in monkeys (Haber et al., 1995; Ferry et al., 2000).
The NAc is thought to be linked to reward mechanisms that not
only modulate motivated behavior towards basic survival needs but also
subserve reinforcement learning in humans more broadly
(O'Doherty 2015).
This is consistent with diffusion MRI (dMRI) tractography in humans and monkeys
(Croxson et al., 2005) that
quantified this brain regions to
be substantially more likely connected to the vmPFC than dmPFC in both species.
Two functional connectivity modalities in humans strongly connected
the vmPFC with the nucleus accumbens, hippocampus (HC),
and posteriomedial cortex.
%
The vmPFC is often proposed to be involved in (external) emotional
reactions and own (visceral) arousal.
Real or imaginged bodily states could be mapped in the vmPFC
as a bioregulatory disposition governing cognition
and decision making (Damasio, 1996; Nauta, 1971)
In neuroeconomic studies of human decision making,
the vmPFC consistently reflects an individual’s subjective
valuation (Behrens et al., 2008; Boorman et al., 2009; Knutson et al., 2005; Plassmann et al., 2007)
This may be why performance within and across participants
was related to state encoding in OFC.
Such a “cognitive map” of action space was argued to encode
the current task state even when states are unobservable from sensory input,
which was shown to be critical for behavior.
The GMV of the vmPFC and nucleus accumbens
correlated with indices of social reward attitudes and
value-guided behavior (Lebreton et al., 2009).
Additionally,
independent whole-brain analyses from structural
neuroimaging studies related the gray-matter volume GMV of the vmPFC,
more consistently than any other
brain region, to indices of
social competence and social network complexity,
among the most complicated decision that humans and monkeys take
(Lebreton et al., 2009; Powell et al., 2010; Lewis et al., 2011; Sallet et al., 2011).
%

@@

Finally,
the right and left TPJ are known to have hemispheric differences
according to their cytoarchitectonic borders and gyrification pattern
(Caspers et al., 2008; Caspers et al., 2006).
Neuroscientific investigations on hemispheric functional specialization
have converged to the right versus left cerebral hemisphere as dominant for
attention versus language functions (Broca 1865, Wernicke 1874, Lichtheim 1885;
Gazzaniga, Bogen et al. 1965, Sperry 1982, Stephan, Marshall et al. 2003).
%
The aRTPJ is a key node network is central for
action initiation during externally structured tasks and
sensorimotor control by integrating supramodal stimulus-guided attention
(Corbetta et al., 2002).
Involvement of this DMN node was repeatedly reported in
visuo-proprioceptive conflict (Balslev et al., 2005) and
multi-modal detection of sensory changes across
visual, auditory, or tactile stimulation in a multi-modal fMRI study
(Downar et al., 2000).
In humans, direct electrical stimulation of the
RTPJ during neurosurgery was associated with altered perception
and stimulus awareness (Blanke et al., 2002).
%
Importantly, the RTPJ has been shown to be intimately related to
supramodal prediction and error signaling.
Neural activity in the RTPJ has been argued to be responsible 
for stimulus-driven attentional reallocation to 
salient and surprising sources of information
as a ‘‘circuit breaker’’ that recalibrates control and maintenance systems
(Bzdok et al., 2013; Corbetta et al., 2008).
Indeed, patients with right TPJ damage have particular difficulties
with multistep actions (Hartmann et al. 2005).
In the face of large discrepancies between actual and previously predicted
environmental events the RTPJ acts a potential switch between
externally-oriented mind sets focussed on the
sensory world and internally-oriented mind sets focussed
on self-relevant mind-wandering of possible mental scenarios.
Transient RTPJ in humans for instance disrupted the
impact of predicted intentions of other individuals (Young et al. 2010b),
a capacity believed to be subserved by the DMN.
The RTPJ might hence be an important player that shifts away
from the default active ‘‘internally directed’’ processes
to deal instead with immediate environmental objects and contexts.
-> (slow) endogeneous changes in state transitions by the policy and value matrices
For example, the alarm at the museum is not part of the task set of listening to the guide’s discussion of Hieronymous Bosch, but it is clearly a behaviourally relevant stimulus. <=> MCMC in HC / PCC

@@

\subsection{Value functions and policies}
The behavior of the agent is governed by some kind of \textit{policy}, which maps states to
sampling probabilities over candidate actions to perform from this state. Starting a time $t=0$,
a policy $\pi$ generates a trajectory as follows
\begin{eqnarray*}
  \begin{split}
    S_1 &\sim \rho(.|S_0,A_0), \text{ collect rewards }R_0 = r(S_0, A_0)\\
    A_1 &\sim \pi(.|S_1)\\
    S_2 &\sim \rho(.|S_1,A_1), \text{ collect rewards }R_1 = r(S_1, A_1)\\
    \ldots\\
    A_{t} &\sim \pi(.|S_{t})\\
    S_{t+1} &\sim \rho(.|S_{t},A_{t}), \text{ collect rewards }R_{t} = r(S_{t}, A_{t})\\
    \ldots
  \end{split}
\end{eqnarray*}
Since an action taken now might have repercussions long into the feature, it turns out that the
quantity to optimize is not the instantaneous rewards $r(s, a)$, but a
cumulative version which takes into account the future. A standard for
modeling this accumulation is the so-called
time-discounted \textit{cumulative reward} function
\begin{equation}
  \label{eq:cumr}
  G^\pi = \sum_{t=0}^{\infty}\gamma^{t}R_t.
\end{equation}
This random variable\footnote{Random as it depends both on the environment's dynamic and the
  policy $\pi$ being played (which can be stochastic).}  measures the cumulative reward of
following a
policy $\pi$. The  goal of RL is then adapt this policy so as to  maximize the cumulative rewards.
In the definition of $G^\pi$ above, the constant $\gamma \in [0, 1]$ is the \textit{discount factor}. The choice $\gamma = 0$   corresponds to a perfectly myopic agent who is solely concerned about their immediate rewards and have no regards for the future. For there to be any learning at all, a technical requirement is that $\gamma < 1$.
% \footnote{In which case we can take $T \rightarrow +\infty$, provided the reward function $r$ is bounded.}.
Thus the agent is positively biased towards considering rewards which are will
come soon. The reward importance hence decays exponentially
with distance in the future,
given that there is more uncertainty in the farsighted future.
The reward discount factor $\gamma$ can thus be seen as calibrating
the delay discounting behavior of the intelligent agent.

@@

By construction, in general, maximizing the expectation in  \eqref{eq:qval} is intractable due to
the enormous number of possible trajectories the agent might need to
consider.
(If the Bellman-based computational ideas have a corresponding
neurobiological implementation, this provides a framework of how
optimal behavior could be computable in the human brain.)
One popular simplification that removes this issue is to only consider the sub-family of
\textit{deterministic policies}, which map each state to the best single best action which
should be taken at thin state, and therefore define functions from states to actions.
\textit{Q-learning} (Watkins \& Dayan, 1992), a commonly used off-policy algorithm, uses the
\textit{greedy policy}
\begin{equation}
  \pi(s) = \argmax_{a \in \mathcal A}{Q}(s, a).
  \label{eq:qlearning}
\end{equation}
% where $\tilde{Q}(s, a)$ is the current estimate of the state-action value
% table.
The celebrated \textit{Bellman's equation} [Sutton and Barto 1998] then takes the simple form
\begin{equation}
  Q^\pi(s, a) = \mathbb E_{s' \sim \rho(.|s,a)} [r(s,a) + \gamma \max_{a' \in \mathcal A}Q^\pi(s', a')]
  = \mathbb E_{s' \sim \rho(.|s,a)} [r(s,a) + \gamma Q^\pi(s', \pi(s'))]
  \label{eq:bellman}
\end{equation}
which provides a recursive decomposition of optimal behavior.
A complicated dynamic programming optimization can be
broken into simpler subproblems at different time points.
It is a fixed-point equation for the deterministic policy $\pi$.
Notice that in the expectation in \eqref{eq:bellman}, the sampling is done over only things which
depend on the environment, and so can be learned off-policy by observing state-transitions
triggered by another behavioral policy, which can be stochastic.

@@

\subsection{Correspondence between DMN function and RL framework}
\textbf{XXX Put the diagrams and process charts here.}
\begin{itemize}
  \item The policy matrix represents the repertoire of possible actions
  on the world given a current state. It encodes the probabilites of
  choosing actions to be executed in a certain situation.
  \item Given a state, the value function represents the estimated utility of
  being in that state, which is subjective to the agent. 
  For a state $s$, the value function at $s$ namely $V(s)$ define provides a quantitative answer to the question:
  "How desirable is it to be in state $s$ ?"
  For each action $a$ that can be taken from state $s$,
  the Q-value  $Q(s, a)$ defined in \eqref{eq:qval} provides the subjective
  utility of executing a specific action; it answers the question
  "What is the expected utiltiy of taking action $a$ in this situation ?"
  \item The DMN may subserve
  constant exploration of possible future actions and their
  cumulative outcomes. Implicit computation of future choices 
  provides an explanation for purposeful mind-wandering.
  \item hippocampus -> provides perturbed action-transition-state-reward samples
  as a block of "imagined", "hypothesized", "recalled" experience;
  the small variations in these experience blocks allow searching
  a larger space of parameters and possible experiences.
  In the absence of environmental input and feedback
  (e.g., mind-wandering or sleep) pseudo-experiencing possible
  future scenarios and action outcomes.
  \item
  \textit{Inference} in the human brain reduces to generalization of
  policy and value adaptations from sampled experiences to
  successful action choices and reward predictions in future states.
  \item In the RL view, plasticity in the DMN arises naturally.
  If an agent behaving optimally in a given environment moves
  to novel, yet unexperienced environments, reward prediction errors will
  massively increase. This will lead to adaptation of the policy matrix
  and value function until the system converges to a
  new steady-state of optimal action decisions given certain states.
  \item The DMN is today known to consistently increase in neural
  activity when engaging cognitive processes that are detached from
  current sensory environment. DMN involvement in thinking about the past,
  the future, and hypothetical possibilities ties in with the
  MDP's implicit computation of action and state cascades as a function
  of what happened in the past.

@@

\section{Relation to other cognitive models (Danilo)}
\paragraph{Predictive Coding and Bayesian Brain Hypothesis}
The predictive coding framework 
is one of the most frequently evoked hypotheses of default mode function.
Cortical responses emerge from a functional network of continuously interacting high and low hierarchical levels,
with a dynamic intercourse that performs inference on the world by reconciling gaps between sensory input and prior information. 
Feed-forward sensory experience is constantly modulated by
modulatory top-down modulation at various hierarchical processing levels.
At each stage of processing abstraction level,
an internally generated prediction of the sensory input is
directly compared against actual external input.
A prediction error, i.e. the difference between sensory input
and internal prediction,
occurring at one of the processing levels
incurs plasticity changes of neuronal back-projections (i.e., model parameters)
for gradually improved future prediction of the environment.
Indeed,
back projection outnumber by far the input projection in the brain
Salin, P.A. and Bullier, J. (1995) Corticocortical connections in the visual system: structure and function. Physiol. Rev. 75, 107–154.
This process permits updates of beliefs about the world
to best fit the incoming sensory examples (Friston2014).
The generative model of how data are generated in the
world would hence be incorporated by
the current neuronal wiring.
Contextual integration is maintained by top-down modulation of sensorimotor
processing by context-specific a-priori information.
formulate perception as a constructive process
based on internal or generative models.

\begin{itemize}
  \item Both accounts are process theories, supported by
  neurobiological evidence, that
  view the brain as a \"statistical organ\" (Friston 2014).
  \item Both have a notion of brain plasticity with increased
  adaption of neuronal wiring when faced by unprecedented environmental
  challenges.
  \item hierarchical aspects from predictive coding in RL lies in the
  nested prediction of probable upcoming actions and rewards
  \item Both model consequences of action. In RL, the horizon of that
  look into the future is manifest in the $\gamma$ parameter, but not
  explicitly modeled in the PC account.
  \item mismatch negativity of PC is immanent in reward prediction error
  by the difference between actually predicted reward of an action given
  a state and the reward predicted by non-linear regression with graded
  discounting of future rewards
  \item Sensory experience is a generative process from both views.
  In predictive coding sensory perception of the external world
  is a generative experience due to modulatory top down experience at
  various hierarchical levels of sensory input processing.
  In RL, the environmental model is incorporated in the Markov decision
  process, \textit{which can be fully recovered based on the last
  state alone}.
  \item Both provide a parsimoneous explanation why
  humans seem to minimize processing of incoming information
  when the environment is predictable and allocate attention when
  novel stimuli are encountered.
  Similarly, the both propose explanations why
  predicting the future is inherently
  linked to information from the past; similarly for independence across
  geographical spaces.
\end{itemize}

@@

@@

\section{Conclusion}
What single brain function could be most important for existence and survival of the species?
Estimating quantities that depend on how features of an agent’s environment are expected to unfold over the future.
From the perspective of the human condition, it remains unclear what the nature and purpose of a domain-overarching computational mechanism implemented in the high association cortex could be to warriant the high energetic costs.

Obtain reward and avoid pain.

The idealized computational framework explains previous observations about the
DMN in a simple in conception but non-trivially links
together disparate functional hypotheses in the DMN literature.

biological plausibility of dynamic optimization in
optimal substructure

; formalize and predict; offer statistical control on the brain's default function/operations

At the least, we propose an alternative vocabulary to
describe and discuss neuroscientific studies on the DMN.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of RL systems. This makes proposed machine-learning
approach to DMN function not only practically computable but
also neuroscientifically falsifiable.
%
The DMN can be viewed as a smoothing kernel extending
from the relatively recent past to the relatively close future
that constantly estimates complex non-linear gain functions.
-> This is why neuroimaging research revealed activity increases in the DMN
when 
-> This may be why perfect memory has been evolutionarily de-selected,
although it is provably feasible by the neurobiological hardware in humans

>>>>

The vmPFC subserves less ambiguous subjective-value-related evaluative processes
reward-informed and risk estimation of self-relevant environmental stimuli.
This DMN node is more closely associated with
orchestrating adapted behavior by bottom-up-driven
processing of “what matters now”,
probably drawing on model-based value representations
\cite{doherty2015structure}.
Quantative lesion findings across 344 human individuals confirmed
a gross impairment in value-based decision making
(Glaescher et al., 2016).
The vmPFC is preferentially connected with limbic and reward-related areas.
The vmPFC has been observed to have monosynaptical connections
with the nucleus accumbens
in axonal tracing studies in monkeys (Haber et al., 1995; Ferry et al., 2000).
The NAc is thought to be linked to reward mechanisms that not
only modulate motivated behavior towards basic survival needs but also
subserve reinforcement learning in humans more broadly
(O'Doherty 2015).
This is consistent with diffusion MRI (dMRI) tractography in humans and monkeys
(Croxson et al., 2005) that
quantified this brain regions to
be substantially more likely connected to the vmPFC than dmPFC in both species.
Two functional connectivity modalities in humans strongly connected
the vmPFC with the nucleus accumbens, hippocampus (HC),
and posteriomedial cortex.
%
The vmPFC is often proposed to be involved in (external) emotional
reactions and own (visceral) arousal.
Real or imaginged bodily states could be mapped in the vmPFC
as a bioregulatory disposition governing cognition
and decision making (Damasio, 1996; Nauta, 1971)
In neuroeconomic studies of human decision making,
the vmPFC consistently reflects an individual’s subjective
valuation (Behrens et al., 2008; Boorman et al., 2009; Knutson et al., 2005; Plassmann et al., 2007)
This may be why performance within and across participants
was related to state encoding in OFC.
Such a “cognitive map” of action space was argued to encode
the current task state even when states are unobservable from sensory input,
which was shown to be critical for behavior.
The GMV of the vmPFC and nucleus accumbens
correlated with indices of social reward attitudes and
value-guided behavior (Lebreton et al., 2009).
Additionally,
independent whole-brain analyses from structural
neuroimaging studies related the gray-matter volume GMV of the vmPFC,
more consistently than any other
brain region, to indices of
social competence and social network complexity,
among the most complicated decision that humans and monkeys take
(Lebreton et al., 2009; Powell et al., 2010; Lewis et al., 2011; Sallet et al., 2011).
%

@@

Finally,
the right and left TPJ are known to have hemispheric differences
according to their cytoarchitectonic borders and gyrification pattern
(Caspers et al., 2008; Caspers et al., 2006).
Neuroscientific investigations on hemispheric functional specialization
have converged to the right versus left cerebral hemisphere as dominant for
attention versus language functions (Broca 1865, Wernicke 1874, Lichtheim 1885;
Gazzaniga, Bogen et al. 1965, Sperry 1982, Stephan, Marshall et al. 2003).
%
The aRTPJ is a key node network is central for
action initiation during externally structured tasks and
sensorimotor control by integrating supramodal stimulus-guided attention
(Corbetta et al., 2002).
Involvement of this DMN node was repeatedly reported in
multi-step action execution \cite{hartmann2005takes},
visuo-proprioceptive conflict (Balslev et al., 2005) and
multi-modal detection of sensory changes across
visual, auditory, or tactile stimulation in a multi-modal fMRI study
(Downar et al., 2000).
In humans, direct electrical stimulation of the
RTPJ during neurosurgery was associated with altered perception
and stimulus awareness (Blanke et al., 2002).
%
Importantly, the RTPJ has been shown to be intimately related to
supramodal prediction and error signaling.
It was argued that the RTPJ encodes actions and ensuing outcomes
without necessarily relating those to outcome value
\cite{liljeholm2013neural, hamilton2008action,
jakobs2009effects}.
Neural activity in the RTPJ has been argued to be responsible 
for stimulus-driven attentional reallocation to 
salient and surprising sources of information
as a ‘‘circuit breaker’’ that recalibrates control and maintenance systems
(Bzdok et al., 2013; Corbetta et al., 2008).
Indeed, patients with right TPJ damage have particular difficulties
with multistep actions (Hartmann et al. 2005).
In the face of large discrepancies between actual and previously predicted
environmental events the RTPJ acts a potential switch between
externally-oriented mind sets focussed on the
sensory world and internally-oriented mind sets focussed
on self-relevant mind-wandering of possible mental scenarios.
Transient RTPJ in humans for instance disrupted the
impact of predicted intentions of other individuals (Young et al. 2010b),
a capacity believed to be subserved by the DMN.
The RTPJ might hence be an important player that shifts away
from the default active ‘‘internally directed’’ processes
to deal instead with immediate environmental objects and contexts.
-> (slow) endogeneous changes in state transitions by the policy and value matrices
For example, the alarm at the museum is not part of the task set of listening to the guide’s discussion of Hieronymous Bosch, but it is clearly a behaviourally relevant stimulus. <=> MCMC in HC / PCC

@@

\subsection{Value functions and policies}
The behavior of the agent is governed by some kind of \textit{policy}, which maps states to
sampling probabilities over candidate actions to perform from this state. Starting a time $t=0$,
a policy $\pi$ generates a trajectory as follows
\begin{eqnarray*}
  \begin{split}
    S_1 &\sim \rho(.|S_0,A_0), \text{ collect rewards }R_0 = r(S_0, A_0)\\
    A_1 &\sim \pi(.|S_1)\\
    S_2 &\sim \rho(.|S_1,A_1), \text{ collect rewards }R_1 = r(S_1, A_1)\\
    \ldots\\
    A_{t} &\sim \pi(.|S_{t})\\
    S_{t+1} &\sim \rho(.|S_{t},A_{t}), \text{ collect rewards }R_{t} = r(S_{t}, A_{t})\\
    \ldots
  \end{split}
\end{eqnarray*}
Since an action taken now might have repercussions long into the feature, it turns out that the
quantity to optimize is not the instantaneous rewards $r(s, a)$, but a
cumulative version which takes into account the future. A standard for
modeling this accumulation is the so-called
time-discounted \textit{cumulative reward} function
\begin{equation}
  \label{eq:cumr}
  G^\pi = \sum_{t=0}^{\infty}\gamma^{t}R_t.
\end{equation}
This random variable\footnote{Random as it depends both on the environment's dynamic and the
  policy $\pi$ being played (which can be stochastic).}  measures the cumulative reward of
following a
policy $\pi$. The  goal of RL is then adapt this policy so as to  maximize the cumulative rewards.
In the definition of $G^\pi$ above, the constant $\gamma \in [0, 1]$ is the \textit{discount factor}. The choice $\gamma = 0$   corresponds to a perfectly myopic agent who is solely concerned about their immediate rewards and has no horizon
for the future. For there to be any learning at all, a technical requirement is that $\gamma < 1$.
% \footnote{In which case we can take $T \rightarrow +\infty$, provided the reward function $r$ is bounded.}.
Thus the agent is positively biased towards considering rewards which are will
come soon. The reward importance hence decays exponentially
with distance in the future,
given that there is more uncertainty in the farsighted future.
The reward discount factor $\gamma$ can thus be seen as calibrating
the delay discounting behavior of the intelligent agent.

@@

By construction, in general, maximizing the expectation in  \eqref{eq:qval} is intractable due to
the enormous number of possible trajectories the agent might need to
consider.
(If the Bellman-based computational ideas have a corresponding
neurobiological implementation, this provides a framework of how
optimal behavior could be computable in the human brain.)
One popular simplification that removes this issue is to only consider the sub-family of
\textit{deterministic policies}, which map each state to the best single best action which
should be taken at thin state, and therefore define functions from states to actions.
\textit{Q-learning} (Watkins \& Dayan, 1992), a commonly used off-policy algorithm, uses the
\textit{greedy policy}
\begin{equation}
  \pi(s) = \argmax_{a \in \mathcal A}{Q}(s, a).
  \label{eq:qlearning}
\end{equation}
% where $\tilde{Q}(s, a)$ is the current estimate of the state-action value
% table.
The celebrated \textit{Bellman's equation} [Sutton and Barto 1998] then takes the simple form
\begin{equation}
  Q^\pi(s, a) = \mathbb E_{s' \sim \rho(.|s,a)} [r(s,a) + \gamma \max_{a' \in \mathcal A}Q^\pi(s', a')]
  = \mathbb E_{s' \sim \rho(.|s,a)} [r(s,a) + \gamma Q^\pi(s', \pi(s'))]
  \label{eq:bellman}
\end{equation}
which provides a recursive decomposition of optimal behavior.
A complicated dynamic programming optimization can be
broken into simpler subproblems at different time points.
Using the Bellman equation, each state can be associated with a certain value,
to guide action (i.e., improve the policy) towards a better state.
It is a fixed-point equation for the deterministic policy $\pi$.
Notice that in the expectation in \eqref{eq:bellman}, the sampling is done over only things which
depend on the environment, and so can be learned off-policy by observing state-transitions
triggered by another behavioral policy, which can be stochastic.

@@

\subsection{Correspondence between DMN function and RL framework}
\textbf{XXX Put the diagrams and process charts here.}
\begin{itemize}
  \item The policy matrix represents the repertoire of possible actions
  on the world given a current state. It encodes the probabilites of
  choosing actions to be executed in a certain situation.
  \item Given a state, the value function represents the estimated utility of
  being in that state, which is subjective to the agent. 
  For a state $s$, the value function at $s$ namely $V(s)$ define provides a quantitative answer to the question:
  "How desirable is it to be in state $s$ ?"
  For each action $a$ that can be taken from state $s$,
  the Q-value  $Q(s, a)$ defined in \eqref{eq:qval} provides the subjective
  utility of executing a specific action; it answers the question
  "What is the expected utiltiy of taking action $a$ in this situation ?"
  \item The DMN may subserve
  constant exploration of possible future actions and their
  cumulative outcomes. Implicit computation of future choices 
  provides an explanation for purposeful mind-wandering.
  \item hippocampus -> provides perturbed action-transition-state-reward samples
  as a block of "imagined", "hypothesized", "recalled" experience;
  the small variations in these experience blocks allow searching
  a larger space of parameters and possible experiences.
  In the absence of environmental input and feedback
  (e.g., mind-wandering or sleep) pseudo-experiencing possible
  future scenarios and action outcomes.
  Our approach acknowledges the unavoidable stochasticity of
  computation in neuronal processes \cite{faisal2008noise}.
  \item
  \textit{Inference} in the human brain reduces to generalization of
  policy and value adaptations from sampled experiences to
  successful action choices and reward predictions in future states.
  \item In the RL view, plasticity in the DMN arises naturally.
  If an agent behaving optimally in a given environment moves
  to novel, yet unexperienced environments, reward prediction errors will
  massively increase. This will lead to adaptation of the policy matrix
  and value function until the system converges to a
  new steady-state of optimal action decisions given certain states.
  \item The DMN is today known to consistently increase in neural
  activity when engaging cognitive processes that are detached from
  current sensory environment. DMN involvement in thinking about the past,
  the future, and hypothetical possibilities ties in with the
  MDP's implicit computation of action and state cascades as a function
  of what happened in the past.

@@

\section{Relation to other cognitive models (Danilo)}
\paragraph{Predictive Coding and Bayesian Brain Hypothesis}
The predictive coding and Bayesian brain framework 
is a frequently evoked idea related to the default mode function
\cite{bar2007}.
Cortical responses emerge from a functional network of continuously interacting high and low hierarchical levels.
A dynamic intercourse performs inference on the world by reconciling gaps between sensory input and prior information. 
Feed-forward sensory experience is constantly modulated by
modulatory top-down modulation at various hierarchical processing levels.
It explains the constructive, generative nature of sensory perception
\cite{friston2010free} and
why motor action is intimately related to sensory expectations
\cite{wolpert1995internal}.
and explains
At each stage of processing abstraction level,
an internally generated prediction of the sensory input is
directly compared against actual external input.
A prediction error, i.e. the difference between sensory input
and internal prediction,
occurring at one of the processing levels
incurs plasticity changes of neuronal back-projections (i.e., model parameters)
for gradually improved future prediction of the environment.
Indeed,
back projection outnumber by far the input projection in the brain
\cite{salin1995corticocortical}.
This process permits updates of beliefs about the world
to best fit the incoming sensory examples.
The generative model of how data are generated in the
world would hence be incorporated by
the current neuronal wiring.
Contextual integration is maintained by top-down modulation of sensorimotor
processing by context-specific a-priori information.
formulate perception as a constructive process
based on internal or generative models.

\begin{itemize}
  \item Both accounts are process theories, supported by
  neurobiological evidence, that
  view the brain as a \"statistical organ\"
  that generalizes from the past to new experiences (Friston 2014).
  \item Both have a notion of brain plasticity with increased
  adaption of neuronal wiring when faced by unprecedented environmental
  challenges.
  \item hierarchical aspects from predictive coding in RL lies in the
  nested prediction of probable upcoming actions and rewards
  \item Both model consequences of action. In RL, the horizon of that
  look into the future is manifest in the $\gamma$ parameter, but not
  explicitly modeled in the PC account.
  \item mismatch negativity of PC is immanent in reward prediction error
  by the difference between actually predicted reward of an action given
  a state and the reward predicted by non-linear regression with graded
  discounting of future rewards
  \item Sensory experience is a generative process from both views.
  In predictive coding sensory perception of the external world
  is a generative experience due to modulatory top down experience at
  various hierarchical levels of sensory input processing.
  In RL, the environmental model is incorporated in the Markov decision
  process, \textit{which can be fully recovered based on the last
  state alone}.
  \item Both provide a parsimoneous explanation why
  humans seem to minimize processing of incoming information
  when the environment is predictable and allocate attention when
  novel stimuli are encountered.
  Similarly, the both propose explanations why
  predicting the future is inherently
  linked to information from the past; similarly for independence across
  geographical spaces.
\end{itemize}

@@

Navigation processes require associative processing to link land- marks with spatial locations, episodic memories require associa- tions for binding the constituents of an episode, emotional processing and the concomitant heightened arousal they entail are tightly associated with affective memories, and our percep- tion of ourselves and others require associations formed with experience to help interpret the present and anticipate the future.
In some respects, predictions may be considered a higher level of thought-element than associations; they also provide the basis to the many processes detailed above as occupying the unconstrained mind (e.g., planning, navigating, anticipating the thoughts and actions of others, stereotyping, imagining our- selves in the future, affective forecasting, etc.). The brain seems to be able to extract regularities and familiar patterns from our environment, and associate them with corresponding knowl- edge in memory to afford the generation of predictions. This idea of predictions as the basis of many, if not most, cognitive processes in the human brain will have to be developed sepa- rately because the observations we described here cannot speak to it directly
Bar2007

@@

\section{Conclusion}
What single brain function could be most important for existence and survival of the species?
Estimating quantities that depend on how features of an agent’s environment are expected to unfold over the future.
From the perspective of the human condition, it remains unclear what the nature and purpose of a domain-overarching computational mechanism implemented in the high association cortex could be to warriant the high energetic costs.
MDP conceptualize control of the environment.
Obtain reward and avoid pain by adaptive behavior.

The idealized computational framework explains previous observations about the
DMN in a simple in conception but non-trivially links
together disparate functional hypotheses in the DMN literature.
The default brain function may be reducible to a small number
of well-defined equations.
biological plausibility of dynamic optimization in
optimal substructure
mathematical formalism; statistical solution; adaptive fitness
; formalize and predict; offer statistical control on the brain's default function/operations
stochastic modelling
At the least, we propose an alternative vocabulary to
describe and discuss neuroscientific studies on the DMN.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of RL systems. This makes proposed machine-learning
approach to DMN function not only practically computable but
also neuroscientifically falsifiable.
%
The DMN can be viewed as a smoothing kernel extending
from the relatively recent past to the relatively close future
that constantly estimates complex non-linear gain functions.
-> This is why neuroimaging research revealed activity increases in the DMN
when 
-> This may be why perfect memory has been evolutionarily de-selected,
although it is provably feasible by the neurobiological hardware in humans
